CF Registry Analysis

### 2024-03-08 Christine Chan/CF Registry/cf_registry_analysis.qmd
forest plots

```{r}
tv_forest_plot <- function(mod, time_varying = NULL, time_variable = "tgroup",
                           labels = labels) {
  coeff <- tbl_regression(mod, pvalue_fun = function(x) x) %>%
    add_n(location = "level") %>%
    add_nevent(location = "level") %>%
    as_tibble()
  # If time-varying, format appropriately
  if (!is.null(time_varying)) {
    # Split table into time-varying and not
    w <- which(coeff$`**Characteristic**` == labels[time_varying])
    coeff <- coeff[w:nrow(coeff), ]
    t <- coeff %>% pivot_longer(`**Characteristic**`)
  }
  coeff_n <- tbl_regression(mod, exponentiate = T) %>%
    add_n(location = "label") %>%
    as_tibble()
  coeff$N2 <- coeff_n$`**N**`
  # Combine Ns
  coeff$N <- pmax(coeff$`**N**`, coeff$N2, na.rm = T)

@@

```{r results='asis'}
invisible(lapply(time_varying, function(v) {
  new_f <- as.formula(paste0(
    y, "~", paste0(x[-which(x == v)], collapse = "+"),
    paste0("+", v, "*strata(tgroup)")
  ))
  cox_res_split <- coxph(new_f, data = s_split, cluster = eDWID)
  cat("\n")
  cat("####", v)
  cat("\n")
  cat("\n")
  plot_df <- tbl_regression(cox_res_split) %>%
    add_n(location = "level") %>%
    add_nevent(location = "level") %>%
    as_tibble()
  plot_df$ll <- as.numeric(sapply(strsplit(plot_df$`**95% CI**`, ", "), "[", 1))
  plot_df$ul <- as.numeric(sapply(strsplit(plot_df$`**95% CI**`, ", "), "[", 2))
  plot_df$hr <- as.numeric(plot_df$`**log(HR)**`)
  plot_df %>%
    forestplot(
      labeltext = c(`**Characteristic**`, `**N**`, `**Event N**`, `**log(HR)**`),
      mean = "hr", lower = "ll", upper = "ul",
      is.summary = is.na(plot_df$`**N**`)
    ) %>%
    fp_add_header(
      `**Characteristic**` = c("", "Characteristic"),
      `**N**` = c("", "N"),
      `**Event N**` = c("", "Event N"),
      `**log(HR)**` = c("", "log(HR)")
    ) %>%
    fp_add_lines() %>%
    fp_set_zebra_style("#EFEFEF", ignore_subheaders = T) %>%
    print()
  cat("\n")
  cat("\n")
}))
```

>>>>

```{r}
tv_forest_plot <- function(mod_coeff, time_variable = NULL, labels = labels) {
  coeff <- tbl_regression(mod, pvalue_fun = function(x) x) %>%
    add_n(location = "level") %>%
    add_nevent(location = "level") %>%
    as_tibble()
  # If time-varying, format appropriately
  if (length(grep("strata", coeff$`**Characteristic**`)) > 0) {
    # Split table into time-varying and not
    w <- which(coeff$`**Characteristic**` == labels[time_varying])
    coeff <- coeff[w:nrow(coeff), ]
    t <- coeff %>% pivot_longer(`**Characteristic**`)
  }
  coeff_n <- tbl_regression(mod, exponentiate = T) %>%
    add_n(location = "label") %>%
    as_tibble()
  coeff$N2 <- coeff_n$`**N**`
  # Combine Ns
  coeff$N <- pmax(coeff$`**N**`, coeff$N2, na.rm = T)

@@

```{r results='asis'}
invisible(lapply(time_varying, function(v) {
  # Formulas
  new_f <- as.formula(paste0(
    y, "~", paste0(x[-which(x == v)], collapse = "+"),
    paste0("+", v, "*strata(tgroup)")
  ))
  new_f_int <- as.formula(paste0(
    y, "~", paste0(x[-which(x == v)], collapse = "+"),
    paste0("+", v, "*tgroup")
  ))
  new_f_emm <- as.formula(paste0(
    "~", paste0(v, "|tgroup")
  ))
  # This could be done more efficiently but it seems to work
  # Fit one stratified model and one with a regular interaction term
  cox_res_split <- coxph(new_f, data = s_split, cluster = eDWID, contrasts = "contr.sum")
  cox_res_split_int <- coxph(new_f_int, data = s_split, cluster = eDWID)
  # Use the regular interaction term to get means for each time period
  cat("\n")
  cat("####", v)
  cat("\n")
  cat("\n")
  cox_res_split %>%
    tbl_regression() %>%
    add_n(location = "level") %>%
    add_nevent(location = "level")
  cat("\n")
  cat("\n")
  cox_res_split %>%
    tbl_regression() %>%
    plot()
  cat("\n")
  cat("\n")
  emm <- data.frame(emmeans(cox_res_split_int, new_f_emm, nuisance = x[-which(x == v)]))
  plot_df <- data.frame(emm) %>% pivot_longer(cols = tgroup, value)

  cat("\n")
  cat("\n")
}))
```
